---
title: "Nielsen Homework 4 MSDS6306"
author: "Heber C. Nielsen, MD"
date: "July 4, 2018"
output: html_document
---
#MSDS 6306 Doing Data Science - Section 404
#Homework Assignment #4
#Heber Nielsen
#
##QUESTION 1: FIVETHIRTYEIGHT DATA
```{r setup}
chooseCRANmirror(graphics=FALSE, ind=1)
knitr::opts_chunk$set(echo = TRUE)
setwd("~/R/R Default Working Folder/Homework_4/Schmoostuff6306")
##
##Parts 1a and 1b
df <- load("C:/Users/Admin/Documents/GitHub/fivethirtyeight/data/college_all_ages.rda")
head (college_all_ages, 4)
df
summary (college_all_ages)
str (college_all_ages)
install.packages("remotes")
library("remotes", lib.loc="~/R/win-library/3.5")
install.packages("plotly")
##install.packages("stringi")
install.packages ("rudeboybert/fivethirtyeight", build_vignettes = TRUE)
browseVignettes (package = "fivethirtyeight")
##
##Part 1c:
### To see a more detailed list of all data sets, see the package vignette
###: vignette("fivethirtyeight", package = "fivethirtyeight")
##
##The related news story is found at this web address: http://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/. The story details the results of analyses of the proportion of college students enrolled in, or recently graduated in, specific majors. These proportions are contrasted with the average earning power of starting positions for individuals with those majors. There is a remarkable difference between what are popular majors and what are better paying jobs. 
##
##Part 1d:
dim(college_all_ages)
head (college_all_ages, 1)
```
---
##QUESTION 2: DATA SUMMARY

---
```{r}
##Part 2a:
df <- data.frame(college_all_ages)
colnames (df)
College_Column_Names <- c(colnames(df))
College_Column_Names
length (College_Column_Names)
##
##Part 2b:
library("plyr", lib.loc="~/R/win-library/3.5")
library("dplyr", lib.loc="~/R/win-library/3.5")
Maj_Cat_Count <- data.frame (unique(df$major_category))
Maj_Cat_Count
major_count <- count (df, "major_category")
major_count
##
##Part 2c:
library("ggplot2", lib.loc="~/R/win-library/3.5")
library("RColorBrewer", lib.loc="~/R/win-library/3.5")
par(las=2)
barplot (major_count$freq, beside = TRUE, horiz = TRUE, col = blues9, border = "black", names.arg = major_count$major_category, main = "Unique College Majors by Discipline", sub = "Number per Discipline", xlab = "Individual Majors", xlim = range(pretty(c(0, major_count$freq))))
##
##Part 2d:
write.csv (college_all_ages, file = "College 538 Data.csv", row.names = FALSE)
```
---
##QUESTION #3: CODEBOOK

###3a:
###The Github repository for my homework is "https://github.com/hebernielsen/SchmooStuff-MSDS-6306"
###3b:
###The README file is in the "SchmooStuff-MSDS-6306" Root Directory. A copy is also in the "Homework 4" subdirectory.
###3c:
###The subdirectory "Homework 4" in "SchmooStuff-MSDS-6306" contains the RMarkdown script, HTML file, and my data file "College 538 Data.csv". The README file credits fivethirtyeight for the data.
###3d:
###This RMarkdown script provides the link to my Github repository.

##QUESTION #4: SWIRL
###The output file for Module 15 of "R Programming" is included in the "Homework 4" subdirectory "Heber Nielsen Homework 4 Swirl 15". Nearly all of the output for this module was graphics, these were not copied into the file. The file gives the module statements and instructions/requests, the code I typed into the module which completed the request, and the progress bars. In the two or three instances that an output other than the graphics was produced, I included that in the output file.
---
